A Graph Theoretic Approach to Problem Formulation for Multidisciplinary Design Analysis and Optimization

### 2013-05-10 conclusions.tex
working on conclusion.

Once a desired FPG is identified, the graph syntax described in the paper can be 
leveraged to formulate a Problem Solution Graph (PSG). This graph includes all of the 
same information from the FPG while additionally describing the particular MDAO 
solution architecture, e.g. MDF, IDF, BLISS, ATC, that will be used to solve the problem.  
Many possible PSGs could be formulated to solve a problem corresponding to a 
specified FPG. The application of the syntax to PSGs has not been illustrated in the paper, 
but the basic concept of applying multiple solution strategies to a given problem 
formulation has been well established by a number of MDAO architecture 
benchmarking efforts\cite{Tedford2009,gray2013}. Furthermore the validity of applying 
graph syntax to the description of specific problem solutions has been demonstrated 
by XDSM.

For simple problems with few analysis tools and variables, the formulation of a valid problem description is straightforward.  
However, MDAO problems continue to grow in scale and complexity.  
As the numbers of analysis tools and variables have increased, it has become increasingly challenging and time consuming for engineering teams to determine how the multiple analysis tools can be interconnected to produce valid problem formulations, to know when other tools must be introduced, and to determine the number of free variables in the problem that can or should be varied by the designer or an optimizer.  
The graph formalism presented in this paper is intended to offer value in this context of increasing problem complexity by providing a formal approach to identify and resolve missing and redundant data in order to create valid MDAO problem formulations.

>>>>

Once a desired FPG is identified, the driver node and driven edge described in the paper can be 
leveraged to formulate a Problem Solution Graph (PSG). This graph includes all of the 
same information from the FPG while additionally describing the particular MDAO 
solution architecture, e.g. MDF, IDF, BLISS, ATC, that will be used to solve the problem.  
Many possible PSGs could be formulated to solve a problem corresponding to a 
specified FPG. The application of the syntax to PSGs has not been illustrated in the paper, 
but the basic concept of applying multiple solution strategies to a given problem 
formulation has been well established by a number of MDAO architecture 
benchmarking efforts. Furthermore the validity of applying 
graph syntax to the description of specific problem solutions has been demonstrated 
by XDSM.

For simple problems with few analysis tools and variables, the formulation of a 
valid problem description is straightforward.  However, MDAO problems continue to 
grow in scale and complexity. As the numbers of analysis tools and variables have 
increased, it has become increasingly challenging and time consuming for engineering 
teams to determine how the multiple analysis tools can be interconnected to produce 
valid problem formulations. Large complex problems also present signficant challenges
as the design process evolves requiring the integration of additional and higher-fidelity 
analysis tools into an existing model. The graph syntax presented in this paper 
is intended to offer value in this context of increasing problem complexity by 
providing a formal approach to identify and resolve data conflicts in a set of interconnected
analysis tools and to help arrange those tools into an effective and efficient system model
where MDAO tools and techniques can be quickly and easily applied.

### 2013-05-10 intro.tex
working on conclusion.

\subsection{Existing Graph-Based Syntax}
	\label{s:existing syntax}
    As indicated in the examples in Sec.~\ref{s:specific vs fundamental}, the mathematical 
    language for specifying problem formulations is very general and can be used both for 
    fundamental and specific problem formulations. Tedford and Martins used this mathematical syntax to specify the 
    FPF for a set of test problems and also to describe specific formulations for solving them with a 
    number of optimization architectures\cite{Tedford2009}. Their work demonstrates how multiple specific 
    problem formulations can relate to a common FPG. The challenge with this 
    traditional mathematical syntax is that it is not easily manipulated or analyzed.

>>>>

\subsection{Existing Graph-Based Syntax}
	\label{s:existing syntax}
    As indicated in the examples in Sec.~\ref{s:specific vs fundamental}, the mathematical 
    language for specifying problem formulations is very general and can be used both for 
    fundamental and specific problem formulations. Tedford and Martins used this mathematical syntax to specify the 
    FPF for a set of test problems and also to describe specific formulations for solving them with a 
    number of optimization architectures\cite{Tedford2009}. This enabled them to produce a set of 
    results benchmarking the performance of different optimziation architectures against a fixed set of 
    problems. Gray et al. also benchmarked the performance of a set of MDAO architectures\cite{Gray2013}. 
    This work looked at a larger set of architectures and proposed the use of OpenMDAO as a platform to begin 
    building a larger community developed set of test problems and architectures. Both benchmarking efforts 
    demonstrate how multiple specific problem formulations can relate to a common FPG and prove the 
    value of a common problem descrition. The challenge with this 
    traditional mathematical syntax is that it is not easily manipulated or analyzed.
